### 2013-12-30 docs/seminar/casestudy.tex
revising seminar

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure\ref{fig:architecture}. The client submits a document and searches translators of a specific target language. Based on query document, the framework figures out offered price, delivery time, proficiency and number of cooperation times related to each translator. The result is processing by a ranking system and the most related translators are offered to the client.

@@

\textit{Ranking} system uses L2R to return the most related translators to the query. The training data is provided by a group of evaluators who are familiar with business of company. In an evaluation system, they choose a translator between three offered ones. In order to prevent bias in evaluation, the translators are offered randomly and without name and picture. Applied method and results are described in Section \ref{sec:apply}. \textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library. The similarity between query and indexed documents is used as a base for estimation of translator's proficiency. In the next step, calculated similarities are aggregated. The applied aggregation function is described in Section \ref{sec:apply}. \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to outperform the response time. The detail of the process is out of scope of the paper .At last, \textit{Profiler} accumulates personal information of translators, their preferences as well as offered price and translation duration per word.

Beside translator, a proofreader selected by the client is revising the final translation. The proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language) as well. The assessment is defined as a value between one (very bad) to five (perfect). As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translation proficiency.

>>>>

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure\ref{fig:architecture}. The client submits a document and searches for translators with a specific target language. Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator. The result is processing by a ranking system and the most related translators are offered to the client.

@@

\textit{Ranking} system uses L2R to return the most related translators to the client. The training data is provided by a group of evaluators who are familiar with business of company using an evaluation system. The evaluation suggests three translators and by comparing between their factors, the evaluators choose one. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section \ref{sec:apply}. \textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library. The similarity between query and indexed documents is used as a base for estimation of translator's proficiency. In order to find a value proficiency, the similarity scores are aggregated. The applied aggregation function is described in Section \ref{sec:apply}. \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to outperform the response time. The detail of the process is out of scope of the paper. At last, \textit{Profiler} accumulates personal information, translators' preferences as well as offered price and translation duration per word.

Beside translator, a proofreader selected by the client revises the final translation. As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language). The assessment is defined as a value between one (very bad) to five (perfect). As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translator's proficiency.

### 2013-12-30 docs/seminar/evaluation.tex
revising seminar

\section{Apply The Methods and Results}
\label{sec:apply}
In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characters and data.

@@

The results of applying Spearman correlation is shown in Table\ref{table:Spearman}. As the outcome shows, GP2 outperforms the other algorithms. In comparison to Top1, Top5 has slightly better performance. The results is also partly the same based on each language-pair.

>>>>

\section{Apply The Methods and Results}
\label{sec:apply}
In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characteristics and data.

@@

The result of applying Spearman correlation is shown in Table\ref{table:Spearman}. As the outcome shows, GP2 outperforms the other algorithms. In comparison to Top1, Top5 has slightly better performance. The results is also partly the same when comparing based on language-pairs.

### 2013-12-30 docs/seminar/introduction.tex
writing case study
revising seminar

The goal of expertise retrieval is to link humans to expertise areas, and vice versa. In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er} \cite{er-community-aware}.

The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects.

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}. Expertise retrieval has received increasing interest since the introduction of an expert finding task in the Text Retrieval Conference (TREC) 2005 \cite{trec2005} \cite{er-community-aware}.

Two principal approaches are proposed in \cite{trec2005} based on probabilistic language modeling techniques. They were formalized as so-called candidate models and document models. the candidate-based approach is also referred to as
profile-based method in builds a textual representation of candidate experts and then rank them based on the query. The document models' idea is to first find documents that are relevant to the topic and then locate the experts associated with these documents \cite{er}.

@@

This paper addresses the problem of searching translators as expertises. We have applied Learning to Rank in a candidate-based approach. Besides, different aggregation algorithms related to documents of translators has been studied.

>>>>

\section{Introduction}
\label{sec:introduction}
The goal of expertise retrieval is to link humans to expertise areas, and vice versa. In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er} \cite{er-community-aware}.

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005} \cite{er-community-aware}.

Two principal approaches are proposed in \cite{trec2005} based on probabilistic language modeling techniques. They were formalized as so-called candidate models and document models. The candidate-based approach which is also referred to as profile-based method, builds a textual representation of candidate experts and then rank them based on the query. The document models is to first find documents that are relevant to the topic and then locate the experts associated with these documents \cite{er}.

@@

This paper addresses the problem of searching translators as experts. We have applied Learning to Rank in a candidate-based approach. Besides, different aggregation algorithms related to documents of translators has been studied.

### 2013-12-30 docs/seminar/methods.tex
revising seminar

\section{Methods}
\label{sec:methods}
In this section, we study thoroughly different methods and algorithms regarding to Aggregation Functions and Learning to Rank. The study will shed light on the problem of picking the most appropriate algorithm regarding to the project.

\subsection{Aggregation Functions}
As a usual scenario in expert retrieval systems, first each document related to an expert is scored and ranked regarding to query. Then, the top $N$ document scores associated with a candidate expert are aggregated in order to rank the experts. The aggregation function has a big impact on the performance of Expert Retrieval system.

The effect of different features on aggregation function is is studied in \cite{agg-gp2}. As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$. Comparing query-based features using statistical measures, it inferred that the features may not, in general, be able to predict the optimal number of documents to aggregate for each query. Individual Expert Features is discussed in the next step. It is shown that relevant experts are associated with a higher ranked document than non-relevant experts. More interestingly, relevant experts are associated with less documents on average.

@@

\subsection{Learning To Rank}
TODO

>>>>

\section{Methods}
\label{sec:methods}
In this section, we study different methods and algorithms regarding to Aggregation Functions and Learning to Rank.

\subsection{Aggregation Functions}
The aggregation function has a significant impact on the performance of Expert Retrieval system. As a usual scenario in expert retrieval systems, first each document related to an expert is scored and ranked regarding to query. Then, the top $N$ document scores associated with a candidate expert are aggregated in order to rank the experts.

The effect of different features on aggregation function is studied in \cite{agg-gp2}. As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$. Comparing query-based features using statistical measures, it inferred that the features may not, in general, be able to predict the optimal number of documents to aggregate for each query. Individual Expert Features is discussed in the next step. It is shown that relevant experts are associated with a higher ranked document than non-relevant experts. More interestingly, relevant experts are associated with less documents on average.

@@

\subsection{Learning To Rank}
Learning to rank refers to machine learning techniques for training the model in a ranking task. Due to its importance, learning to rank has been drawing broad attention in the machine learning community recently. 
TODO
